Technical Report

### 2024-02-16 Reports/tech_report1.tex
Update report

@@

>>>>

\subsubsection*{Results.} No meaningful result. The $\gamma$ is still 0.24007008332521998.

\subsection{Seek the best open ReLU number for layer 3 for normal 5x100}

This experiment is to find the best open ReLU number for layer 3 normal 5x100 with new hyperplane constraints: previous open 17 node is based on old constraints.

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number.py|. And the partial output file name is \verb*|Gamma_5x100_normal_layer3_seek_openrelu.txt|.  It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 3 with different open ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 021600202024

	\item\emph{Open $\ReLU$ number:} Open 15,18,21,24,27 ReLU nodes for each node.

	\item\emph{Processes:} 20 processes in parallel. Do node 0 to 19 each 5 cases.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_15_11_40_01.b|; this file stores all alpha beta gamma of nodes of all layers for the same network (gamma is up to layer 5). 
\end{itemize}

Most is the same as Feb 15's experiments.

@@

Not finished before stop, but it is very obvious that 21 is the best among all 5 cases.
